---
title: "Plotly"
output: 
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	message = FALSE
)
```

I am going to make some plotly plots based on [NY NOAA](https://p8105.com/dataset_noaa.html).


## Load packages and data

```{r}
library(tidyverse)
library(p8105.datasets)
library(plotly)
library(RColorBrewer)
```


Let's get some data and preprocess it.

```{r}
data("ny_noaa")

set.seed(12345)

ny_noaa_sub = ny_noaa %>% 
  sample_frac(0.25) %>% 
  separate(date, into = c("year", "month", "day"), sep = "-", remove = FALSE) %>% 
  mutate(
    year = as.numeric(year),
    month = as.numeric(month),
    day = as.numeric(day),
    prcp = ifelse(!is.na(prcp), prcp / 10, NA_real_),
    tmax = ifelse(!is.na(tmax), as.numeric(tmax) / 10, NA_real_),
    tmin = ifelse(!is.na(tmin), as.numeric(tmin) / 10, NA_real_)
  ) %>% 
  filter(year %in% 2000:2010)
```

There are `r nrow(ny_noaa)` observations in the `ny_noaa` dataset. To get a smaller dataset, I would like to take a 25% random sample (`ny_noaa_sub`) from it and further narrow down the data to observations from 2000 to 2010.


## Plotly line plot

```{r}
ny_noaa_sub %>% 
  mutate(
    date = format(as.Date(date, format = "%Y-%m-%d"), "%Y-%m")
  ) %>% 
  group_by(date) %>% 
  summarise(
    mean_tmin = mean(tmin, na.rm = TRUE)
  ) %>% 
  plot_ly(
    x = ~ date,
    y = ~ mean_tmin,
    type = "scatter",
    mode = "lines"
  ) %>% 
  layout(
    title = "Monthly Average Minimum Temperature from 2000 to 2010",
    xaxis = list(title = "Date"),
    yaxis = list(title = "Average Minimum Temperature\n(degrees C)")
  )
```

This line plot shows the monthly average minimum temperature from 2000 to 2010 in `ny_noaa`'s 25% random sample dataset.


## Plotly box plot

```{r}
ny_noaa_sub %>% 
  mutate(
    month = factor(month.name[month], levels = month.name)
  ) %>% 
  plot_ly(
    x = ~ month,
    y = ~ tmax,
    color = ~ month,
    type = "box",
    colors = "Set2"
  ) %>% 
  layout(
    title = "Distribution of Maximum Temperature by Month",
    xaxis = list(title = "Month"),
    yaxis = list(title = "Maximum Temperature\n(degrees C)"),
    legend = list(title = list(text = "Month"))
  )
```

This box plot shows the distribution of maximum temperature by month.


## Plotly bar plot

```{r}
ny_noaa_sub %>% 
  distinct(id, year, month, .keep_all = TRUE) %>% 
  group_by(year, month) %>% 
  count() %>% 
  mutate(
    month = factor(month.name[month], levels = month.name, ordered = TRUE)
  ) %>% 
  plot_ly(
    x = ~ year,
    y = ~ n,
    color = ~ month,
    type = "bar",
    colors = "viridis",
    alpha = .8
  ) %>% 
  layout(
    barmode = "stack",
    title = "Number of Weather Stations Functioning by Year",
    xaxis = list(title = "Year"),
    yaxis = list(title = "Number of Weather Stations"),
    legend = list(title = list(text = "Month"))
  )
```

This bar plot shows the number of unique weather stations in each year in `ny_noaa`'s 25% random sample dataset. Within each year, the monthly number is also provided. We can tell that the number of weather stations included in this dataset tend to increase.


## Dashboard

A dashboard displaying these plots can be found [here](dashboard.html).
